---
title: "Creating Functions for the Data Generation and Analysis"
format: html
---

# 1. Functions to Generate Data

## 1.1 Generating Formulas from a Parameters List

```{r}
generate_formula <- function(parameters) {
  terms <- c("1") # Start with intercept
  
  for (name in names(parameters)) {
    # Detect interaction terms
    if (grepl(":", name)) {
      # Split interaction terms
      components <- strsplit(name, ":")[[1]]
      
      # Process each part of interaction
      processed_components <- sapply(components, function(component) {
        if (grepl("^difference_", component)) {
          var <- sub("^difference_", "", component)
          return(paste0("difference('", var, "', scaling = 'std')"))
        } else if (grepl("^same_", component)) {
          var <- sub("^same_", "", component)
          return(paste0("same('", var, "')"))
        } else if (grepl("^send_", component)) {
          var <- sub("^send_", "", component)
          return(paste0("send('", var, "', scaling = 'std')"))
        } else if (grepl("^receive_", component)) {
          var <- sub("^receive_", "", component)
          return(paste0("receive('", var, "', scaling = 'std')"))
        } else if (grepl("^tie_", component)) {
          var <- sub("^tie_", "", component)
          return(paste0("tie('", var, "', scaling = 'std')"))
        } else if (grepl("^average_", component)) {
          var <- sub("^average_", "", component)
          return(paste0("average('", var, "', scaling = 'std')"))
        } else if (grepl("^minimum_", component)) {
          var <- sub("^minimum_", "", component)
          return(paste0("minimum('", var, "', scaling = 'std')"))
        } else if (grepl("^maximum_", component)) {
          var <- sub("^maximum_", "", component)
          return(paste0("maximum('", var, "', scaling = 'std')"))
        } else if (grepl("^event_", component)) {
          var <- sub("^event_", "", component)
          return(paste0("event('", var, "')"))
        } else if (grepl("^userStat_", component)) {
          var <- sub("^userStat_", "", component)
          return(paste0("userStat('", var, "')"))
        } else if (component == "inertia") {
          return("inertia(scaling = 'std')")
        } else if (component == "indegreeSender") {
          return("indegreeSender(scaling = 'std')")
        } else if (component == "indegreeReceiver") {
          return("indegreeReceiver(scaling = 'std')")
        } else if (component == "outdegreeSender") {
          return("outdegreeSender(scaling = 'std')")
        } else if (component == "outdegreeReceiver") {
          return("outdegreeReceiver(scaling = 'std')")
        } else if (component == "totaldegreeDyad") {
          return("totaldegreeDyad(scaling = 'std')")
        } else if (component == "totaldegreeSender") {
          return("totaldegreeSender(scaling = 'std')")
        } else if (component == "totaldegreeReceiver") {
          return("totaldegreeReceiver(scaling = 'std')")
        } else if (component == "degreeMin") {
          return("degreeMin(scaling = 'std')")
        } else if (component == "degreeMax") {
          return("degreeMax(scaling = 'std')")
        } else if (component == "degreeDiff") {
          return("degreeDiff(scaling = 'std')")
        } else if (component == "sp") {
          return("sp(scaling = 'std')")
        } else if (component == "reciprocity") {
          return("reciprocity(scaling = 'std')")
        } else if (component == "otp") {
          return("otp(scaling = 'std')")
        } else if (component == "itp") {
          return("itp(scaling = 'std')")
        } else if (component == "osp") {
          return("osp(scaling = 'std')")
        } else if (component == "isp") {
          return("isp(scaling = 'std')")
        } else if (component == "psABBA") {
          return("psABBA()")
        } else if (component == "psABBY") {
          return("psABBY()")
        } else if (component == "psABXA") {
          return("psABXA()")
        } else if (component == "psABXB") {
          return("psABXB()")
        } else if (component == "psABXY") {
          return("psABXY()")
        } else if (component == "psABAY") {
          return("psABAY()")
        } else if (component == "psABAB") {
          return("psABAB()")
        } else if (component == "rrankSend") {
          return("rrankSend()")
        } else if (component == "rrankReceive") {
          return("rrankReceive()")
        } else if (component == "recencySendSender") {
          return("recencySendSender()")
        } else if (component == "recencySendReceiver") {
          return("recencySendReceiver()")
        } else if (component == "recencyReceiveSender") {
          return("recencyReceiveSender()")
        } else if (component == "recencyReceiveReceiver") {
          return("recencyReceiveReceiver()")
        } else if (component == "recencyContinue") {
          return("recencyContinue()")
        } else if (component == "FEtype") {
          return("FEtype()")
        } else {
          return("") # Handle or skip any unrecognized components
        }
      })
      
      # Add interaction terms by joining effects with `:`
      terms <- c(terms, paste(processed_components, collapse = " : "))
      
    } else if (name == "inertia") {
      terms <- c(terms, "inertia(scaling = 'std')")
    } else if (grepl("^difference_", name)) {
      var <- sub("^difference_", "", name)
      terms <- c(terms, paste0("difference('", var, "', scaling = 'std')"))
    } else if (grepl("^same_", name)) {
      var <- sub("^same_", "", name)
      terms <- c(terms, paste0("same('", var, "')"))
    } else if (grepl("^send_", name)) {
      var <- sub("^send_", "", name)
      terms <- c(terms, paste0("send('", var, "', scaling = 'std')"))
    } else if (grepl("^receive_", name)) {
      var <- sub("^receive_", "", name)
      terms <- c(terms, paste0("receive('", var, "', scaling = 'std')"))
    } else if (grepl("^tie_", name)) {
      var <- sub("^tie_", "", name)
      terms <- c(terms, paste0("tie('", var, "', scaling = 'std')"))
    } else if (grepl("^average_", name)) {
      var <- sub("^average_", "", name)
      terms <- c(terms, paste0("average('", var, "', scaling = 'std')"))
    } else if (grepl("^minimum_", name)) {
      var <- sub("^minimum_", "", name)
      terms <- c(terms, paste0("minimum('", var, "', scaling = 'std')"))
    } else if (grepl("^maximum_", name)) {
      var <- sub("^maximum_", "", name)
      terms <- c(terms, paste0("maximum('", var, "', scaling = 'std')"))
    } else if (grepl("^event_", name)) {
      var <- sub("^event_", "", name)
      terms <- c(terms, paste0("event('", var, "')"))
    } else if (grepl("^userStat_", name)) {
      var <- sub("^userStat_", "", name)
      terms <- c(terms, paste0("userStat('", var, "')"))
    } else if (name == "indegreeSender") {
      terms <- c(terms, "indegreeSender(scaling = 'std')")
    } else if (name == "indegreeReceiver") {
      terms <- c(terms, "indegreeReceiver(scaling = 'std')")
    } else if (name == "outdegreeSender") {
      terms <- c(terms, "outdegreeSender(scaling = 'std')")
    } else if (name == "outdegreeReceiver") {
      terms <- c(terms, "outdegreeReceiver(scaling = 'std')")
    } else if (name == "totaldegreeDyad") {
      terms <- c(terms, "totaldegreeDyad(scaling = 'std')")
    } else if (name == "totaldegreeSender") {
      terms <- c(terms, "totaldegreeSender(scaling = 'std')")
    } else if (name == "totaldegreeReceiver") {
      terms <- c(terms, "totaldegreeReceiver(scaling = 'std')")
    } else if (name == "degreeMin") {
      terms <- c(terms, "degreeMin(scaling = 'std')")
    } else if (name == "degreeMax") {
      terms <- c(terms, "degreeMax(scaling = 'std')")
    } else if (name == "degreeDiff") {
      terms <- c(terms, "degreeDiff(scaling = 'std')")
    } else if (name == "sp") {
      terms <- c(terms, "sp(scaling = 'std')")
    } else if (name == "reciprocity") {
      terms <- c(terms, "reciprocity(scaling = 'std')")
    } else if (name == "otp") {
      terms <- c(terms, "otp(scaling = 'std')")
    } else if (name == "itp") {
      terms <- c(terms, "itp(scaling = 'std')")
    } else if (name == "osp") {
      terms <- c(terms, "osp(scaling = 'std')")
    } else if (name == "isp") {
      terms <- c(terms, "isp(scaling = 'std')")
    } else if (name == "psABBA") {
      terms <- c(terms, "psABBA()")
    } else if (name == "psABBY") {
      terms <- c(terms, "psABBY()")
    } else if (name == "psABXA") {
      terms <- c(terms, "psABXA()")
    } else if (name == "psABXB") {
      terms <- c(terms, "psABXB()")
    } else if (name == "psABXY") {
      terms <- c(terms, "psABXY()")
    } else if (name == "psABAY") {
      terms <- c(terms, "psABAY()")
    } else if (name == "psABAB") {
      terms <- c(terms, "psABAB()")
    } else if (name == "rrankSend") {
      terms <- c(terms, "rrankSend()")
    } else if (name == "rrankReceive") {
      terms <- c(terms, "rrankReceive()")
    } else if (name == "recencySendSender") {
      terms <- c(terms, "recencySendSender()")
    } else if (name == "recencySendReceiver") {
      terms <- c(terms, "recencySendReceiver()")
    } else if (name == "recencyReceiveSender") {
      terms <- c(terms, "recencyReceiveSender()")
    } else if (name == "recencyReceiveReceiver") {
      terms <- c(terms, "recencyReceiveReceiver()")
    } else if (name == "recencyContinue") {
      terms <- c(terms, "recencyContinue()")
    } else if (name == "FEtype") {
      terms <- c(terms, "FEtype()")
    }
  }
  
  # Combine terms to formula
  formula_text <- paste("~", paste(terms, collapse = " + "))
  formula <- as.formula(formula_text)
  return(formula)
}
```

## 1.2 Generating Data

```{r}
generate_rem <-function (parameters, # parameters for the model
                         covar, #  data frame with id, time, and covariates
                         M, # number of events
                         directed = FALSE # directed or undirected network
                         ) 
{
  # Generate the formula
  formula <- generate_formula(parameters)
  j = 1
  t <- 0 # time of first event
  dummy <- data.frame(time = 1, actor1 = 1, actor2 = 2) # create dummy first event
  rehOut <-remify::remify(edgelist = dummy,model = "tie",actors = covar$name,
                          directed = directed,origin = 0) # remify the dummy
  
  out <- remstats(reh = rehOut, tie_effects = formula, attr_actors  = covar) # compute statistics
  riskset<-attributes(out)$riskset # get the riskset
  adj <- matrix(0, 1, ncol = nrow(riskset)) # adjacency matrix
  
  
    param=parameters
    
    for (i in 1:M) {
      
      beta <- lapply(param, function(x) {
        if (class(x) == "function") {
          x(t)
        }
        else {
          x
        }
      })
      logLambda <- out[dim(out)[1],,] %*% unlist(beta) # log of the rate parameter
      
      lambda <- exp(logLambda) # rate parameter
      dt <- rexp(1, sum(lambda)) # time to next event
      d <- sample(1:nrow(lambda), 1, prob = lambda/sum(lambda)) # next event
      if (i+((j-1)*M) == 1) {
        # initialize edgelist for the first event
        edgelist <- cbind(time = (t + dt), actor1 = riskset[d, 
                                                            1], actor2 = riskset[d, 2])
      }
      else {
        # bind the new event to the edgelist for next events
        edgelist <- rbind(edgelist, cbind(time = (t + dt), 
                                          actor1 = riskset[d, 1], actor2 = riskset[d, 
                                                                                   2]))
      }
      edgelist <- as.data.frame(edgelist) # convert to data frame
      edgelist$time <- as.numeric(edgelist$time) # convert time to numeric
      t <- max(edgelist$time) # update time
      adj <- rbind(adj, adj[i+((j-1)*M), ]) # add a row to the adjacency matrix
      adj[i + 1+((j-1)*M), d] <- adj[i + 1+((j-1)*M), d] + 1 # update the adjacency matrix (1 for the event)
      cat(i+((j-1)*M), "\r") # print the current iteration
      if (i < M) {
        dummy$time <- dummy$time + t # update the time of the dummy event
        edgelistTemp <- rbind(edgelist, dummy) # create temp edgelist to calculate endo stats
        rehOut <-remify::remify(edgelist = edgelistTemp, model = "tie",actors = covar$name,
                                directed = directed,origin = 0) # remify the temp edgelist
        
        
        
        if ( i+((j-1)*M)<= M ){
          out <- remstats(reh = rehOut, tie_effects = formula, attr_actors  = covar) # calculate endo stats
          } 
        else{
          stop<-  i+((j-1)*M)
          start<- i+((j-1)*M)-M+1
          
          out <- remstats(reh = rehOut, tie_effects = formula, attr_actors = covar,memory = "full",start =start, stop =stop , memory_value=400 )
        }
      }
    }
  edgelist
}
```

# 2. Functions for Estimating the Models

## 2.1 Subsetting Generated Edgelists

```{r}
subset_edgelists <- function(edgelists, m) {
  for (i in seq_along(edgelists)) {
    edgelists[[i]] <- edgelists[[i]][1:m,]
  }
  return(edgelists)
}
```

## 2.2 Estimating Models

```{r}
estimate_models <- function(edgelists, num_cores, parameters, covar) {
  set.seed(123)
  
  # Parallel processing with mclapply
  results <- parallel::mclapply(seq_along(edgelists), function(i) {
    tryCatch({
      effects <- generate_formula(parameters)
      reh <- remify(edgelists[[i]], directed = TRUE, model = "tie")
      statistics <- remstats(reh = reh, tie_effects = effects, attr_actors = covar)
      fit <- remstimate::remstimate(reh = reh, stats = statistics, method = "MLE", timing = "interval")
      
      coefs <- summary(fit)$coefsTab
      selected_vars_mle_05 <- rownames(coefs[coefs[, 4] < 0.05,])
      selected_vars_mle_01 <- rownames(coefs[coefs[, 4] < 0.01,])
      
      estimates <- coef(fit)
      cov <- fit$vcov
      cov[upper.tri(cov)] <- t(cov)[upper.tri(cov)]
      
      # Horsehoe
      shrink_hs <- shrinkem(estimates, cov, type = "horseshoe")
      coefs_shrink_hs <- summary(shrink_hs)
      selected_vars_shrink_hs <- rownames(coefs_shrink_hs[coefs_shrink_hs$nonzero == 1,])
      
      # Ridge
      shrink_ridge <- shrinkem(estimates, cov, type = "ridge")
      coefs_shrink_ridge <- summary(shrink_ridge)
      selected_vars_shrink_ridge <- rownames(coefs_shrink_ridge[coefs_shrink_ridge$nonzero == 1,])
      
      list(
        mle_coefs = coefs, 
        selected_vars_mle_05 = selected_vars_mle_05,
        selected_vars_mle_01 = selected_vars_mle_01,
        shrink_hs = shrink_hs,
        shrink_ridge = shrink_ridge,
        shrink_coefs_hs = coefs_shrink_hs,
        shrink_coefs_ridge = coefs_shrink_ridge,
        selected_vars_shrink_hs = selected_vars_shrink_hs,
        selected_vars_shrink_ridge = selected_vars_shrink_ridge
      )
    }, error = function(e) {
      list(
        mle_coefs = NULL, 
        selected_vars_mle_05 = NULL,
        selected_vars_mle_01 = NULL,
        shrink_coefs_hs = NULL,
        shrink_coefs_ridge = NULL,
        selected_vars_shrink_hs = NULL,
        selected_vars_shrink_ridge = NULL
      )
    })
  }, mc.cores = num_cores)
  
  # Combine results into separate lists
  list(
    mle_coefs = lapply(results, `[[`, "mle_coefs"),
    selected_vars_mle_05 = lapply(results, `[[`, "selected_vars_mle_05"),
    selected_vars_mle_01 = lapply(results, `[[`, "selected_vars_mle_01"),
    shrink_hs = lapply(results, `[[`, "shrink_hs"),
    shrink_ridge = lapply(results, `[[`, "shrink_ridge"),
    shrink_coefs_hs = lapply(results, `[[`, "shrink_coefs_hs"),
    shrink_coefs_ridge = lapply(results, `[[`, "shrink_coefs_ridge"),
    selected_vars_shrink_hs = lapply(results, `[[`, "selected_vars_shrink_hs"),
    selected_vars_shrink_ridge = lapply(results, `[[`, "selected_vars_shrink_ridge")
  )
}

estimate_edgelists <- function(edgelists, parameters, covar, num_cores, m) {
  # apply subset edgelists for all m in vector m
  edgelists_subsetted <- lapply(m, function(m) subset_edgelists(edgelists, m))
  names(edgelists_subsetted) <- paste0("m=", m) # name the list elements
  
  # estimate models for all m in vector m
  results <- lapply(edgelists_subsetted, function(edgelists) estimate_models(edgelists, num_cores, parameters, covar))
  
  # combine results into a list
  return(results)
}
```

# 3. Functions for Data Analysis

## 3.1 Variable Selection


### 3.1.1 Function for True Discovery Rate

```{r}
discovery_rate <- function(parameters,
                           estimates,
                           m,
                           edgelists,
                           estimation = c("mle_05", "mle_01", "shrink_hs", "shrink_ridge"),
                           coefficients) {
  
  estimation <- match.arg(estimation) # check that input is valid
  
  # Extract coefficients and settings
  all_coefficients <- names(parameters)
  num_iterations <- length(edgelists)
  num_coefficients <- length(all_coefficients)
  
  # Generate data frame
  data <- data.frame(
    m = rep(m, each = num_coefficients * num_iterations),
    Iteration = rep(1:num_iterations, each = num_coefficients),
    Coefficient = rep(all_coefficients, times = length(m)),
    selected = "not selected"
  )
  
  # Populate selected coefficients
  for (i in seq_along(m)) {
    m_key <- paste0("m=", m[i])
    if (m_key %in% names(estimates)) {
      for (j in 1:num_iterations) {
        selected_key <- paste0("selected_vars_", estimation)
        selected_vars <- estimates[[m_key]][[selected_key]][[j]]
        
        # Check for non-NULL and non-empty entries
        if (!is.null(selected_vars) && length(selected_vars) > 0) {
          data$selected[data$m == m[i] &
                               data$Iteration == j &
                               data$Coefficient %in% selected_vars] <- "selected"
        }
      }
    }
  }
  
  # Create the plot
  discovery_rate <- data %>%
    mutate(
      Coefficient = factor(Coefficient, levels = c(
        names(parameters[parameters != 0]), names(parameters[parameters == 0])
      )),
      selected = factor(selected, levels = c("not selected", "selected"))
    ) %>%
    filter(Coefficient %in% coefficients) %>%
    group_by(m) %>%
    summarise(
      selected = sum(selected == "selected"),
      total = n(),
      discovery_rate = selected / total
    ) %>%
    ungroup()
  
  data <- data %>%
    mutate(
      Coefficient = factor(Coefficient, levels = c(
        names(parameters[parameters != 0]), names(parameters[parameters == 0])
      )),
      selected = selected == "selected") %>%
    filter(Coefficient %in% coefficients)
  
  return(list(discovery_rate = discovery_rate$discovery_rate, 
              data = data))
}  
```

### 3.1.2 Function to Plot True Discovery Rate

```{r}
plot_true_discovery_rates <- function(data) {
  # Melt data frame
  melted_data <- reshape2::melt(
    data,
    id.vars = "m",
    variable.name = "Method",
    value.name = "TrueDiscoveryRate"
  )
  
  # Set custom colors
  color_palette <- c("#D55E00", "#0072B2", "#009E73", "#CC79A7")
  
  # Create plot
  ggplot2::ggplot(
    melted_data,
    ggplot2::aes(
      x = m,
      y = TrueDiscoveryRate,
      group = Method,
      shape = Method,
      linetype = Method,
      color = Method
    )
  ) +
    ggplot2::geom_line(linewidth = 1) +
    ggplot2::geom_point(size = 2.5) +
    ggplot2::ylim(0, 1) +
    ggplot2::scale_x_continuous(breaks = c(100, 200, 400, 800, 1600, 3200)) +
    ggplot2::labs(x = "Events (M)", y = "True Discovery Rate") +
    ggplot2::theme_minimal() +
    ggplot2::theme(
      plot.title = ggplot2::element_text(hjust = 0.5),
      axis.title.x = ggplot2::element_text(size = 14),
      axis.text.x = ggplot2::element_text(
        angle = 45,
        hjust = 1,
        size = 10
      ),
      axis.title.y = ggplot2::element_text(size = 14),
      axis.text.y = ggplot2::element_text(size = 12),
      legend.title = ggplot2::element_text(size = 14),
      legend.text = ggplot2::element_text(size = 12)
    ) +
    ggplot2::scale_shape_manual("Selection Criterion",
      values = c(16, 17, 15, 18),
      labels = c("\u03B1 = 0.05 (MLE)", "95% HDI (ABR HS)", "95% HDI (ABR Ridge)")
    ) +
    ggplot2::scale_linetype_manual("Selection Criterion",
      values = c("solid", "dotted", "longdash"),
      labels = c("\u03B1 = 0.05 (MLE)", "95% HDI (ABR HS)", "95% HDI (ABR Ridge)")
    ) +
    ggplot2::scale_colour_manual("Selection Criterion",
      values = color_palette,
      labels = c("\u03B1 = 0.05 (MLE)", "95% HDI (ABR HS)", "95% HDI (ABR Ridge)")
    )
}

```


### 3.1.3 Function to Plot False Discovery Rate

```{r}
plot_false_discovery_rates <- function(data) {
  # Melt the data frame
  melted_data <- reshape2::melt(
    data,
    id.vars = "m",
    variable.name = "Method",
    value.name = "FalseDiscoveryRate"
  )
  
  # Set custom colors
  color_palette <- c("#D55E00", "#0072B2", "#009E73", "#CC79A7")
  
  # Create plot
  ggplot2::ggplot(
    melted_data,
    ggplot2::aes(
      x = m,
      y = FalseDiscoveryRate,
      group = Method,
      shape = Method,
      linetype = Method,
      color = Method
    )
  ) +
    ggplot2::geom_line(linewidth = 1) +
    ggplot2::geom_point(size = 2.5) +
    ggplot2::ylim(0, 0.35) +
    ggplot2::scale_x_continuous(breaks = c(100, 200, 400, 800, 1600, 3200)) +
    ggplot2::labs(x = "Events (M)", y = "False Discovery Rate") +
    ggplot2::theme_minimal() +
    ggplot2::theme(
      plot.title = ggplot2::element_text(hjust = 0.5),
      axis.title.x = ggplot2::element_text(size = 14),
      axis.text.x = ggplot2::element_text(
        angle = 45,
        hjust = 1,
        size = 10
      ),
      axis.title.y = ggplot2::element_text(size = 14),
      axis.text.y = ggplot2::element_text(size = 12),
      legend.title = ggplot2::element_text(size = 14),
      legend.text = ggplot2::element_text(size = 12)
    ) +
    ggplot2::scale_shape_manual("Selection Criterion",
      values = c(16, 17, 15, 18),
      labels = c("\u03B1 = 0.05 (MLE)", "95% HDI (ABR HS)", "95% HDI (ABR Ridge)")
    ) +
    ggplot2::scale_linetype_manual("Selection Criterion",
      values = c("solid", "dotted", "longdash"),
      labels = c("\u03B1 = 0.05 (MLE)", "95% HDI (ABR HS)", "95% HDI (ABR Ridge)")
    ) +
    ggplot2::scale_colour_manual("Selection Criterion",
      values = color_palette,
      labels = c("\u03B1 = 0.05 (MLE)", "95% HDI (ABR HS)", "95% HDI (ABR Ridge)")
    )
}

```

### 3.1.4 Function to Plot Selected Variables

```{r}
significance_plot <- function(parameters,
                              estimates,
                              m,
                              edgelists,
                              estimation = c("mle_05", "mle_01", "shrink_hs", "shrink_ridge")) {
  # Check that estimation is valid
  estimation <- match.arg(estimation)
  
  # Get coefficients and settings
  all_coefficients <- names(parameters)
  num_iterations <- length(edgelists)
  num_coefficients <- length(all_coefficients)
  
  # Create data frame
  plot_data <- data.frame(
    m = rep(m, each = num_coefficients * num_iterations),
    Iteration = rep(1:num_iterations, each = num_coefficients),
    Coefficient = rep(all_coefficients, times = length(m)),
    selected = "not selected"
  )
  
  # Populate selected coefficients
  for (i in seq_along(m)) {
    m_key <- paste0("m=", m[i])
    if (m_key %in% names(estimates)) {
      for (j in 1:num_iterations) {
        selected_key <- paste0("selected_vars_", estimation)
        selected_vars <- estimates[[m_key]][[selected_key]][[j]]
        
        # Check for non-NULL and non-empty entries
        if (!is.null(selected_vars) && length(selected_vars) > 0) {
          plot_data$selected[plot_data$m == m[i] &
                               plot_data$Iteration == j &
                               plot_data$Coefficient %in% selected_vars] <- "selected"
        }
      }
    }
  }
  
  # Create the plot
  plot_data_processed <- plot_data %>%
    mutate(
      Coefficient = factor(Coefficient, levels = c(
        names(parameters[parameters != 0]), names(parameters[parameters == 0])
      )),
      selected = factor(selected, levels = c("not selected", "selected")),
      fill_label = case_when(
        selected == "not selected" ~ "Not Selected",
        selected == "selected" &
          Coefficient %in% names(parameters[parameters != 0]) ~ "Correctly Selected",
        selected == "selected" &
          Coefficient %in% names(parameters[parameters == 0]) ~ "Falsely Selected"
      ),
      fill_color = case_when(
        selected == "not selected" ~ "lightgray",
        selected == "selected" &
          Coefficient %in% names(parameters[parameters != 0]) ~ "darkgreen",
        selected == "selected" &
          Coefficient %in% names(parameters[parameters == 0]) ~ "darkred"
      ),
      x_order = factor(paste0("m=", m, ", Iter=", Iteration), levels = unlist(lapply(unique(m), function(m)
        paste0("m=", m, ", Iter=", 1:num_iterations))))
    )
  
  plot <- ggplot(plot_data_processed,
         aes(x = x_order, y = Coefficient, fill = fill_label)) +
    geom_tile(color = "white") +
    geom_hline(
      yintercept = length(names(parameters[parameters != 0])) + 0.5,
      linetype = "dashed",
      color = "black"
    ) +
    geom_vline(
      xintercept = cumsum(rep(num_iterations, length(m))) + 0.5,
      linetype = "dashed",
      color = "black"
    ) +
    scale_fill_manual(
      values = c(
        "Not Selected" = "lightgray",
        "Correctly Selected" = "darkgreen",
        "Falsely Selected" = "darkred"
      ),
      name = "Effect Type"
    ) +
    labs(
      title = paste(
        "Significance of Coefficients Across Models and Iterations (",
        estimation,
        ")",
        sep = ""
      ),
      x = "Model and Iteration",
      y = "Coefficient"
    ) +
    theme_minimal() +
    theme(axis.text.x = element_text(
      angle = 90,
      hjust = 1,
      vjust = 0.5
    ))
  
  
  return(list(plot_data = plot_data_processed, plot = plot))
}
```

## 3.2 Effect Sizes

### 3.2.1 Function for Bias and Variance of the Effect Sizes

```{r}
bias_estimates <- function(parameters,
                           estimates,
                           m = c(100, 200, 400, 800, 1600, 3200),
                           method = c("shrink_coefs_hs", "shrink_coefs_ridge", "mle_coefs")) {
  # Extract coefficients and settings
  all_coefficients <- names(parameters)
  num_iterations <- length(edgelists)
  num_coefficients <- length(all_coefficients)
  
  # Extract true coefficients
  true <- unlist(parameters)
  names(true) <- names(parameters)
  
  # Create data frame
  data <- as.data.frame(matrix(NA, nrow = length(m) * num_iterations * num_coefficients, ncol = 4))
  
  colnames(data) <- c("m", "iteration", "coefficient", "bias")
  
  for (i in seq_along(m)) {
    m_key <- paste0("m=", m[i])
    for (j in 1:num_iterations) {
      selected_key <- method
      if (selected_key == "mle_coefs") {
        estimate <- estimates[[m_key]][[selected_key]][[j]][, 1]
      } else {
        estimate <- estimates[[m_key]][[selected_key]][[j]][, 4]
      }
      
      start_index <- ((i-1)*(num_iterations*num_coefficients)+(j-1)*num_coefficients+1)
end_index <- start_index + num_coefficients - 1
index <- start_index:end_index

bias <- estimate - true

      data$m[index] <- m[i]
      data$iteration[index] <- j
      data$coefficient[index] <- names(parameters)
      data$bias[index] <- if (length(bias) == 0 || is.null(bias)) NA else bias
    }
  }
  
  return(data)
}

```


## 3.3 Predictive Performance

### 3.3.1 Predictive Performance for One Edgelist

```{r}
predictive_performance_all <- function(edgelist,
                                   covar,
                                   coefficients,
                                   reh,
                                   statistics,
                                   quantile = 0.95,
                                   warnings = TRUE) {
  top5 <- rep(FALSE, nrow(edgelist))
  
  if (!warnings) {
    suppressWarnings({
      for (i in 1:nrow(edgelist)) {
        
        # Calculate event rates for every actor in R
        lambda <- exp(as.numeric(statistics[i,,] %*% coefficients))
        
        # Extract top 5% of lambdas row indices
        top_5_lambda <- which(lambda > quantile(lambda, quantile))
        # extract specific dyad that belongs to this row
        top_5_dyads <- getDyad(x = reh, dyadID = top_5_lambda)[,2:3]
        
        actual <- edgelist[i,c(2,3)]
        
        # Check if actual is part of top_5_dyads
        top5[i] <- nrow(merge(actual, top_5_dyads)) > 0
      }
    })
  } else {
    
    for (i in 1:nrow(edgelist)) {
      
      lambda <- exp(as.numeric(statistics[i,,] %*% coefficients))
      
      # Extract top 5% of lambdas row indices
      top_5_lambda <- which(lambda > quantile(lambda, quantile))
      # extract specific dyad that belongs to this row
      top_5_dyads <- getDyad(x = reh, dyadID = top_5_lambda)[,2:3]
      
      actual <- edgelist[i,c(2,3)]
      
      # Check if actual is part of top_5_dyads
      top5[i] <- nrow(merge(actual, top_5_dyads)) > 0
    }
  }
  
  return(top5 = sum(top5)/nrow(edgelist))
}
```


### 3.3.2 In-Sample Predictive Performance for All Edgelists

```{r}
pp_is_all <- function(edgelists, m, parameters, covar, estimates, quantile = 0.95) {
  # Data frame to store results
  pp_all <- as.data.frame(matrix(NA, nrow = length(edgelists) * length(m), ncol = 5))
  colnames(pp_all) <- c("m", "iteration", "mle", "ridge", "hs")

  # Loop over each edgelist
  for (j in seq_along(edgelists)) {
    # Prepare the remify and remstats objects
    reh <- remify(edgelists[[j]],
                  directed = TRUE,
                  model = "tie",
                  riskset = "full")
    statistics <- remstats(
      reh = reh,
      tie_effects = generate_formula(parameters),
      attr_actors = covar
    )

    # Loop over each value of m
    for (i in seq_along(m)) {
      m_key <- paste0("m=", m[i])
      row <- (i - 1) * length(edgelists) + j
      pp_all[row, 1] <- m[i]
      pp_all[row, 2] <- j

      # Calculate predictive performance for MLE
      pp_all[row, 3] <- tryCatch({
        predictive_performance_all(
          edgelist = edgelists[[j]][1:m[i], ],
          covar = covar,
          coefficients = estimates[[m_key]][["mle_coefs"]][[j]][, 1],
          reh = reh,
          statistics = statistics,
          quantile = quantile
        )
      }, error = function(e) {
        NA
      })

      # Calculate predictive performance for ridge
      pp_all[row, 4] <- tryCatch({
        predictive_performance_all(
          edgelist = edgelists[[j]][1:m[i], ],
          covar = covar,
          coefficients = estimates[[m_key]][["shrink_coefs_ridge"]][[j]][, 4],
          reh = reh,
          statistics = statistics,
          quantile = quantile,
          warnings = FALSE
        )
      }, error = function(e) {
        NA
      })

      # Calculate predictive performance for horseshoe
      pp_all[row, 5] <- tryCatch({
        predictive_performance_all(
          edgelist = edgelists[[j]][1:m[i], ],
          covar = covar,
          coefficients = estimates[[m_key]][["shrink_coefs_hs"]][[j]][, 4],
          reh = reh,
          statistics = statistics,
          quantile = quantile,
          warnings = FALSE
        )
      }, error = function(e) {
        NA
      })
    }
  }

  return(pp_all)
}

```

### 3.3.3 Out-of-Sample Predictive Performance for All Edgelists

```{r}
pp_oos_all <- function(edgelists, m, parameters, covar, estimates, quantile = 0.95, new = 500) {
  # Data frame to store results
  pp_all <- as.data.frame(matrix(NA, nrow = length(edgelists) * length(m), ncol = 5))
  colnames(pp_all) <- c("m", "iteration", "mle", "ridge", "hs")

  # Loop over each edgelist
  for (j in seq_along(edgelists)) {
    # Prepare the remify and remstats objects
    reh <- remify(edgelists[[j]],
                  directed = TRUE,
                  model = "tie",
                  riskset = "full")
    statistics <- remstats(
      reh = reh,
      tie_effects = generate_formula(parameters),
      attr_actors = covar
    )

    # Loop over each value of m
    for (i in seq_along(m)) {
      m_key <- paste0("m=", m[i])
      row <- (i - 1) * length(edgelists) + j
      pp_all[row, 1] <- m[i]
      pp_all[row, 2] <- j
      
      edgelist_oos <- edgelists[[j]][(m[i]+1):(m[i]+new), ]

      # Calculate predictive performance for MLE
      pp_all[row, 3] <- tryCatch({
        predictive_performance_all(
          edgelist = edgelist_oos,
          covar = covar,
          coefficients = estimates[[m_key]][["mle_coefs"]][[j]][, 1],
          reh = reh,
          statistics = statistics,
          quantile = quantile,
          warnings = FALSE
        )
      }, error = function(e) {
        NA
      })

      # Calculate predictive performance for ridge
      pp_all[row, 4] <- tryCatch({
        predictive_performance_all(
          edgelist = edgelist_oos,
          covar = covar,
          coefficients = estimates[[m_key]][["shrink_coefs_ridge"]][[j]][, 4],
          reh = reh,
          statistics = statistics,
          quantile = quantile,
          warnings = FALSE
        )
      }, error = function(e) {
        NA
      })

      # Calculate predictive performance for horseshoe (hs)
      pp_all[row, 5] <- tryCatch({
        predictive_performance_all(
          edgelist = edgelist_oos,
          covar = covar,
          coefficients = estimates[[m_key]][["shrink_coefs_hs"]][[j]][, 4],
          reh = reh,
          statistics = statistics,
          quantile = quantile,
          warnings = FALSE
        )
      }, error = function(e) {
        NA
      })
    }
  }

  return(pp_all)
}
```

### 3.3.4 Function to Generate LaTeX Tables

```{r}
pp_latex <- function(pp_data) {
  latex_table <- pp_data %>%
    group_by(m) %>%
    summarise(
      pp_mle = round(mean(mle, na.rm = TRUE), 3),
      pp_ridge = round(mean(ridge, na.rm = TRUE), 3),
      pp_hs = round(mean(hs, na.rm = TRUE), 3)
    ) %>%
    rowwise() %>%
    mutate(
      max_value = max(c(pp_mle, pp_ridge, pp_hs), na.rm = TRUE),
      pp_mle = ifelse(
        pp_mle == max_value,
        kableExtra::cell_spec(pp_mle, "latex", bold = TRUE),
        as.character(pp_mle)
      ),
      pp_ridge = ifelse(
        pp_ridge == max_value,
        kableExtra::cell_spec(pp_ridge, "latex", bold = TRUE),
        as.character(pp_ridge)
      ),
      pp_hs = ifelse(
        pp_hs == max_value,
        kableExtra::cell_spec(pp_hs, "latex", bold = TRUE),
        as.character(pp_hs)
      )
    ) %>%
    select(-max_value) %>%
    ungroup() %>%
    kableExtra::kable(
      format = "latex",
      escape = FALSE,
      col.names = c("Events (M)", "MLE", "Ridge", "HS"),
      caption = "Predictive Performance for Different Models and Events (M)",
      booktabs = TRUE
    ) %>%
    kableExtra::kable_styling(full_width = FALSE)
  
  return(latex_table)
}

```

### 3.3.4 Function for Predictive Performance Plots

```{r}
plot_pp <- function(pp) {
  # Helper function for labels
  custom_labels <- function(value) {
    paste0("Top ", (1 - as.numeric(value)) * 100, "%")
  }
  
  # Melt the data for ggplot
  melted_pp <- melt(
    pp,
    id.vars = c("m", "quantile"),
    variable.name = "Method",
    value.name = "Value"
  )
  
  # Set colors
  color_palette <- c("#D55E00", "#0072B2", "#009E73")
  
  # Create plot
  plot <- ggplot(
    melted_pp,
    aes(
      x = m,
      y = Value,
      group = Method,
      shape = Method,
      linetype = Method,
      color = Method
    )
  ) +
    geom_line(linewidth = 1) +
    geom_point(size = 2.5) +
    scale_x_continuous(
      breaks = c(100, 200, 400, 800, 1600, 3200),
      labels = c("100", "200", "400", "800", "1600", "3200"),
      limits = c(0, 3200)
    ) +
    ylim(0.88, 1) +
    labs(x = "Events (M)", y = "Predictive Performance", ) +
    theme_minimal() +
    theme(
      plot.title = element_text(hjust = 0.5, size = 14),
      axis.title.x = element_text(size = 12),
      axis.text.x = element_text(
        angle = 45,
        hjust = 1,
        size = 8.5
      ),
      axis.title.y = element_text(size = 12),
      axis.text.y = element_text(size = 10),
      legend.title = element_text(size = 12),
      legend.text = element_text(size = 10),
      legend.position = "bottom",
      strip.text = element_text(size = 14)
    ) +
    scale_shape_manual("Model",
                        values = c(16, 17, 15),
                       labels = c("MLE", "ABR HS", "ABR Ridge")) +
    scale_linetype_manual("Model",
      values = c("solid", "dotted", "longdash"),
      labels = c("MLE", "ABR HS", "ABR Ridge")
    ) +
    scale_colour_manual("Model",
                        values = color_palette,
                        labels = c("MLE", "ABR HS", "ABR Ridge")) +
    facet_wrap( ~ quantile, labeller = labeller(quantile = custom_labels))
  
  return(plot)
}
```



# 3. Save the Functions

```{r}
save.image("functions.RData")
```

